Preliminary categorisation of SpaceWarps candidates

### 2016-04-08 paper2.tex
clean up images

% Only include extra packages if you really need them. Common packages are:
\usepackage[dvipdfmx]{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{bmpsize}

@@

\lenstitle{SW01 (ASW0004dv8)}
  This is some text that says somwthing more than this line.

@@

\subsection{convincing}
\begin{itemize}
  \item SW02 (ASW000619d) \\

  \item SW05 (ASW0007k4r) \\

  \item SW09 (ASW0002asp) \\

  \item SW28 (ASW0007xrs) \\

  \item SW29 (ASW0008qsm) \\

@@

% The best way to enter references is to use BibTeX:
\bibliographystyle{mnras}
\bibliography{bib/bibli} % if your bibtex file is called example.bib

>>>>

% Only include extra packages if you really need them. Common packages are:
\usepackage[dvipdfmx]{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
%\usepackage{bmpsize}

% I disabled hyperlink in the cls und included it here because of bugs
\usepackage{hyperref}   % Hyperlinks
\hypersetup{colorlinks=true,linkcolor=blue,citecolor=blue,filecolor=blue,urlcolor=blue}

@@

\lenstitle{SW01 (ASW0004dv8)}
  This is some text that says something more than this line.

@@

\subsection{convincing}
\begin{itemize}
  \item SW02 (ASW000619d)

  \item SW05 (ASW0007k4r)

  \item SW09 (ASW0002asp)

  \item SW28 (ASW0007xrs)

  \item SW29 (ASW0008qsm)

@@

% The best way to enter references is to use BibTeX:
\bibliographystyle{mnras}
\bibliography{bib/bibli.bib} % if your bibtex file is called example.bib
